Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-03-04 paper/paper1/ms.tex
Ok, figures are looking good!

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_WASP69_transfer_learned.png}
    \caption{Semi-empirical model of WASP 69 transfer-learned with \texttt{blas\'e}. }
    \label{fig_WASP69_transferred}
\end{figure}

>>>>

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_WASP69_regularized.png}
    \caption{Semi-empirical model of WASP 69 transfer-learned with \texttt{blas\'e}, employing a regularization prior on the learned amplitudes.}
    \label{fig_WASP69_transferred}
\end{figure}

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{figures/blase_super_resolution_template.png}
    \caption{The native-resolution semi-empirical model transfer-learned from WASP 69 HPF data. The revised model can be viewed as a super-resolution deconvolution of the HPF spectrum.}
    \label{fig_WASP69_regularized}
\end{figure}
